### 2019-11-23 monograph/chapters/object_beautifier.tex
Fixed the SingleSpaceFormatter variables names

    def format_text(self, matched_text, matched_setting):
        matched_text = matched_text.strip( " " )

        if matched_setting:
            return " " * matched_setting + matched_text + " " * matched_setting
        else:
            return matched_text
\end{minted}
\end{code}
\end{bluebox}
\end{quadro}

>>>>

    def format_text(self, code_to_format, setting_value):
        code_to_format = code_to_format.strip( " " )

        if setting_value:
            return " " * setting_value + code_to_format + " " * setting_value
        else:
            return code_to_format
\end{minted}
\end{code}
\end{bluebox}
\end{quadro}
